---
title: "{{{package}}}: Reporting Statistics"
output: html_document
date: "2023-03-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

{{#anyPkgs}}

```{r,include=TRUE,results="hide",message=FALSE,warning=FALSE}
library(BiocPkgTools)
library(BiocPkgStats)
library(lubridate)
```
```{r}
package <- "{{{package}}}"
gh_org <- "{{{org}}}"
gh_repo <- paste(gh_org, package, sep = "/")
pkgType <- typeTranslate("{{{pkgType}}}")
packageType <- typeEnglish(pkgType)
```

```{r}
## Release Download Rank
since_date <- as_date("{{{sinceDate}}}")
smonth <- month(since_date, abbr = FALSE, label = TRUE)
syear <- year(since_date)
dlrank <- pkgDownloadRank(pkg = package, pkgType = pkgType, version = "3.16")
dlrank <- round(dlrank, 0)
```

```{r}
now <- year(Sys.time())
## Average Downloads
dls <- pkgDownloadStats(package, pkgType = pkgType, years = syear:now)
avgdls <- mean(dls[["Nb_of_distinct_IPs"]])
avgdls <- round(avgdls, 0)
```

```{r}
## Number of reverse dependencies
db <- available.packages(repos = BiocManager::repositories())
revdeps <- tools::package_dependencies(
    packages = package, db = db, reverse = TRUE, which = "all"
)[[1]]
totalrd <- length(revdeps)
```

```{r}
## Activity since date
## Issues closed: 
suppressMessages({
    activity <- activitySince(
        gh_repo,
        "issues",
        "closed",
        since_date
    )
})
nclosed <- nrow(activity)
nclosed <-
    paste0(nclosed, " ", if (identical(nclosed, 1L)) "issue" else "issues")
```

```{r}
## Commits made:
suppressMessages({
    commitact <- activitySince(
        gh_repo,
        "commits",
        Date = since_date
    )
})
ncommits <- nrow(commitact)
ncommits <-
    paste0(ncommits, " ", if (identical(ncommits, 1L)) "commit" else "commits")
```

{{{package}}} is in the top `r dlrank`% most downloaded `r packageType` packages
in Bioconductor, averaging about `r avgdls` downloads per month since `r smonth`
`r syear`. About `r totalrd` Bioconductor packages depend on {{{package}}} in
either their Depends, Imports, or Suggests fields. We have closed  `r nclosed`
on GitHub relating to questions and improvements to the {{{package}}}
infrastructure from the community and created `r ncommits`
to the software to provide additional functionality and documentation.

{{/anyPkgs}}
