---
title: "{{{package}}}: Reporting Statistics"
output: html_document
date: "2023-03-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

{{#anyPkgs}}

```{r,include=TRUE,results="hide",message=FALSE,warning=FALSE}
library(BiocPkgTools)
library(lubridate)
```
```{r}
package <- "{{{package}}}"
gh_org <- "{{{org}}}"
gh_repo <- paste(gh_org, package, sep = "/")
```

```{r}
bv <- packageDescription(pkg = package)$biocViews
terms <- unlist(strsplit(packageDescription(package)$biocViews, ",\\s+|\n"))
type <- biocViews::guessPackageType(terms)
```

```{r}
typeTranslate <- function(type_term) {
    # integrate with BiocPkgTools:::repo_short_names?
    result <- switch(
        type_term,
        Software = "software",
        ExperimentData = "data-experiment",
        AnnotationData = "data-annotation",
        Workflow = "workflows",
        NULL
    )
    if (is.null(result))
        stop("Term could not be matched")
    result
}
pkgType <- typeTranslate(type)
```

```{r}
typeEnglish <- function(package_type) {
    if (endsWith(package_type, "s"))
        package_type <-
            substr(package_type, nchar(package_type), nchar(package_type))
    gsub("-", " ", package_type)
}
packageType <- typeEnglish(pkgType)
```

```{r}
## Release Download Rank
since_date <- as_date("{{{sinceDate}}}")
smonth <- month(since_date, abbr = FALSE, label = TRUE)
syear <- year(since_date)
dlrank <- pkgDownloadRank(pkg = package, pkgType = pkgType, version = "3.16")
dlrank <- round(dlrank, 0)
```

```{r}
## Average Downloads
dls <- pkgDownloadStats(package, pkgType = pkgType, years = 2021:2023)
avgdls <- mean(dls[["Nb_of_distinct_IPs"]])
avgdls <- round(avgdls, 0)
```

```{r}
## Number of reverse dependencies
db <- available.packages(repos = BiocManager::repositories())
revdeps <- tools::package_dependencies(
    packages = package, db = db, reverse = TRUE, which = "all"
)[[1]]
totalrd <- length(revdeps)
```

```{r}
## Activity since date
## Issues closed: 
activity <- activitySince(
    gh_repo,
    "issues",
    "closed",
    since_date
)
nclosed <- nrow(activity)
nclosed <-
    paste0(nclosed, " ", if (identical(nclosed, 1L)) "issue" else "issues")
```

```{r}
## Commits made:
commitact <- activitySince(
    gh_repo,
    "commits",
    Date = since_date
)
ncommits <- nrow(commitact)
ncommits <-
    paste0(ncommits, " ", if (identical(ncommits, 1L)) "commit" else "commits")
```

## {{{package}}}

{{{package}}} is in the top `r dlrank`% most downloaded `r packageType` packages
in Bioconductor, averaging about `r avgdls` downloads per month since `r smonth`
`r syear`. About `r totalrd` Bioconductor packages depend on {{{package}}} in
either their Depends, Imports, or Suggests fields. We have closed  `r nclosed`
on GitHub relating to questions and improvements to the {{{package}}}
infrastructure from the community and created `r ncommits` commits
to the software to provide additional functionality and documentation.

{{/anyPkgs}}
